Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-11 inc/design_considerations/considerations.tex
as I have suspected, the only previous model I need to introduce is the AG model.
This commit changes the introductions of several chapters and lowers the headings by one in the new AG model chapter

In Chapters \ref{chap:previous_models} through \ref{chap:model_results}, I have explored the mathematical side of designing an ultrafast electron microscope; modeling the behavior of a pulse and the effects that column elements have upon it.
However, since microscopy is an experimental science, we are also designing and building a prototype UEM system at UIC.
In doing so we have decided that special care must be given to the creation and propagation of the electron beam.
In the case of single-shot UEM, in which the image of the sample is acquired using only one electron pulse, several factors lead to two major considerations: first, that a large area photoemission source is required to smaller area or even single point emitters, and second, that the ``normalized transverse emittance,'' a beam quality figure of merit which will be defined later, must be minimized.

>>>>

In Chapters \ref{chap:ms_model} through \ref{chap:model_results}, I have explored the mathematical side of designing an ultrafast electron microscope; modeling the behavior of a pulse and the effects that column elements have upon it.
However, since microscopy is an experimental science, we are also designing and building a prototype UEM system at UIC.
In doing so we have decided that special care must be given to the creation and propagation of the electron beam.
In the case of single-shot UEM, in which the image of the sample is acquired using only one electron pulse, several factors lead to two major considerations: first, that a large area photoemission source is required to smaller area or even single point emitters, and second, that the ``normalized transverse emittance,'' a beam quality figure of merit which will be defined later, must be minimized.

### 2013-04-11 inc/ms_model/ms_model.tex
as I have suspected, the only previous model I need to introduce is the AG model.
This commit changes the introductions of several chapters and lowers the headings by one in the new AG model chapter

\section{The Analytic Gaussian Model} \label{sec:ms_model}

This section introduces the Analytic Gaussian (AG) model of Michalik and Sipe~\cite{michalik_analytic_2006}.
In the AG model the dynamics of a Gaussian electon pulse are computed using a mean-field self-similar approximation.
The result is a set of equations that can be solved very quickly using numerical methods on a modern computer.
When checked against N-body simulations, the authors find that the model is also surprisingly accurate, even for a large set of non-Gaussian pulses~\cite{michalik_analytic_2006,michalik_evolution_2009}.

The only force included in the AG model is that of the internal repulsive space-charge field.
In Chapter \ref{chap:extension}, I will extend this model, adding the influence of external forces, making it more generally applicable for UEM.

\subsection{Formal Evolution} \label{sec:formal_evolution}

@@

\subsection{Evolution of a Gaussian Distribution}

@@

\subsection{Generating the Differential Equations}

@@

\subsection{The Differential Equation System}

@@

\subsection{Validity and Limitations}

>>>>

This chapter introduces the Analytic Gaussian (AG) model of Michalik and Sipe~\cite{michalik_analytic_2006}.
In the AG model the dynamics of a Gaussian electon pulse are computed using a mean-field self-similar approximation.
The result is a set of equations that can be solved very quickly using numerical methods on a modern computer.
When checked against N-body simulations, the authors find that the model is also surprisingly accurate, even for a large set of non-Gaussian pulses~\cite{michalik_analytic_2006,michalik_evolution_2009}.

A drawback of this model is that the only force included is that of the internal repulsive space-charge field.
In Chapter \ref{chap:extension}, I will extend this model, adding the influence of external forces, making it more generally applicable for UEM.

\section{Formal Evolution} \label{sec:formal_evolution}

@@

\section{Evolution of a Gaussian Distribution}

@@

\section{Generating the Differential Equations}

@@

\section{The Differential Equation System}

@@

\section{Validity and Limitations}

### 2013-04-11 main.tex
flattened model_results section headings, removing free-space versus forced
remove (essentially) unused \inputdata command, which was meant to ignore loading tikz data
reconstitute mytikz as a package, with option external to handle this stuff
be more careful with default external handling
added rf cavity comparison plot (like figs 5(a)/6(a) from JAP paper)
I have a title!
added single photon section and basic plot
more work on single_photon section
improve symbolic consistency between este paper derived sections and the rest of the paper
killing more TODOs
began working on a conclusion sectio

\usepackage{graphicx}
\graphicspath{{./images/}}
\DeclareGraphicsExtensions{.png,.pdf,.jpg}
\input{mytikz}
\setboolean{inputdata}{true}
\usepackage{fancyvrb}
\input{pygments}

@@

\title{Title}
\author{Joel Berger}
\pdegrees{of the\\University of Illinois at Chicago}
\degree{Doctor of Philosophy in Physics}

@@

\tableofcontents
\listoftables
\listoffigures

@@

\chapter{Review of Foundational Modeling Efforts} \label{chap:previous_models}

@@

Modeling a system as complex as an Ultrafast Electron Microscope is an enourmous task.
In Chapter \ref{chap:previous_models}, I have highlighted some previous efforts at modeling electron pulse evolution.
While these are excellent works in their own right, none provide the complete picture of the evolution of an electron pulse through the entire column.
In the following chapter, I will present a model which builds on and extends those individual pieces to form a single model; one which is generic enough to model many different columns and is computationally fast enough to be used to design and optimize a column.

@@

  %TODO refer from here to Free expansion results

@@

\section{Free Expansion Propagation}

@@

\section{Propagtion under External Forces}

@@

@@

\section{Flat Metal Photocathodes}

@@

>>>>

\usepackage{graphicx}
\graphicspath{{./images/}}
\DeclareGraphicsExtensions{.png,.pdf,.jpg}

\usepackage[noexternal]{mytikz}

\usepackage{fancyvrb}
\input{pygments}

@@

\title{Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling}
\author{Joel Berger}
\pdegrees{of the\\University of Illinois at Chicago}
\degree{Doctor of Philosophy in Physics}

@@

\tableofcontents
%\listoftables
\listoffigures

@@

  \subimport{inc/}{introduction}

\chapter{The Analytic Gaussian Model} \label{chap:ms_model}

@@

  \subimport{inc/extension/}{introduction}

@@

@@

@@

@@

  \subimport{inc/model_results/rf_cav/}{rf_cav}

@@

  \subimport{inc/photocathode/single_photon/}{single_photon}

  \subimport{inc/photocathode/two_photon_thermionic/}{two_photon_thermionic}

@@

  \subimport{inc/photocathode/}{future}

\chapter{Conclusions}

  \subimport{inc/}{conclusions}
